---
title: "CS 422"
output: 
  html_notebook:
    toc: yes
    toc_float: yes
author: Vijay K. Gurbani, Ph.D., 
        Illinois Institute of Technology
---

<!-- More information in R Markdown can be found at:
1. https://www.ssc.wisc.edu/sscc/pubs/RFR/RFR_RMarkdown.html  This is 
   the place to start since it is a short tutorial.
2. https://rmarkdown.rstudio.com/index.html This contains a longer 
   tutorial.  Take a look at the cheatsheet in 
   https://rmarkdown.rstudio.com/lesson-15.html, it is a concise 
   reference of R Markdown on two pages.
<-->

## Use this as a template for your homeworks.
#### Run all the chunks by clicking on "Run" at the top right of the edit 
#### window and choose "Run All".  Assuming there were no errors in the
#### chunk, you should see a "Preview" button become visible on the top
#### left of the edit window.  Click this button and a html document should
#### pop up with the output from this R markdown script.

### Part 1-A
```{r}
setwd("/tmp")
data(cars)
cars
```

### Part 1-B

```{r}
plot(cars, main="The Cars Dataset")
```
### Part 1-C (Summary)
```{r}
summary(cars)
```

### Part 1-D
```{r}
summ <- summary(cars)
max.speed.str <- summ[,1][6]
max.speed.str <- strsplit(max.speed.str, ":")
max.speed <- max.speed.str[[1]][2]

min.dist.str <- summ[,2][1]
min.dist.str <- strsplit(min.dist.str, ":  ")
min.dist <- min.dist.str[[1]][2]

str <- paste0("Maximum speed is ", max.speed, ", and minimum distance is ", 
              min.dist)
str
```



